---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oqthemes

<!-- badges: start -->
<!-- badges: end -->

A theme library for **orderlyquant** work (ggplot2, Rmarkdown, etc)

## Goals

- create a theme package that suits my aesthetic tastes and keeps
  me from fiddling around during data analysis
- become more familiar with the package creation process, including:
  - tests
  - documentation

## Background

- package development process followed the notes
  [here](https://www.notion.so/Snippets-fb64b41b178148e98ff94286e3c26619#59b119faf2164f79b30c41bf1837c461)
- heavily influenced by the package design of `hrbrthemes`
- also shaped by ideas found in [`cr`](https://github.com/connorrothschild/cr)
  and [`tpltheme`](https://github.com/connorrothschild/cr) from Connor Rothschild


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("orderlyquant/oqthemes")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(oqthemes)
## basic example code
##
## not run:
## <some ggplot2 object> + scale_color_oq()
```
